Domain-agnostic Outlier Ranking Algorithms (DORA)---A Configurable Pipeline for Facilitating Outlier Detection in Scientific Datasets

### 2021-09-18 publications/iaai21/dora_outlier_detection_iaai.tex
Add discussion of evaluation metrics and experiments. #42

\paragraph{Evaluation in outlier detection.}  \todo{Discuss why evaluation
in outlier detection applications is hard since we often don't have complete
labeled data for testing and labels can be subjective.}

>>>>

\paragraph{Evaluation in outlier detection.} Prior work has emphasized
the difficulty of creating standardized metrics for outlier detection that 
represents how models will perform in real world settings while also enabling
intercomparison between datasets~\cite{campos2016evaluation}. We chose two
complementary metrics with this in mind: precision at $N=n_{outliers}$, which
measures the fraction of selections that are known outliers when the number of
selections is equivalent to the number of outliers, and
 Mean Discovery Rate, which measures the fraction of selections that are known outliers on average. 
Designing experiments to evaluate outlier detection methods for real-world
use cases is also difficult because it is difficult, or sometimes impossible, 
to obtain labeled samples of outliers, inliers, or both for evaluation. 
In addition, labels are often subjective or uncertain, 
especially in the case of scientific datasets. For example, a dataset of known
outliers was available for the astrophysics dataset from human annotation
in prior work, but the remainder of samples in the dataset used for evaluation
were not known to be inliers or outliers. This can result in evaluation metrics
 that are deceptively low because unlabeled samples that might actually be
 outliers (as was found to be common in prior work~\cite{wagstaff:des-anom20})
 are counted as false positives.
